---
title: "Banking From First Principles"
author: "Rob Carnell"
date: 'Rev 0.2, `r strftime(Sys.time(), "%d %b %Y")` '
output: html_document
---

```{r setup, include=FALSE, echo=FALSE}
require(rvest)
require(lubridate)
require(ggplot2)
require(plotly)
require(assertthat)
require(waterfalls)

if (tolower(Sys.info()["user"]) == "hb82795")
{
  httr::set_config(config = httr::config(proxy = "hnbproxy.hban.us", proxyport = 3128L, 
                                        use_ssl = 0L, ssl_verifypeer = 0L, 
                                        ssl_verifyhost = 0L, ssl_verifystatus = 0L, 
                                        proxy_ssl_verifyhost = 0L, 
                                        proxy_ssl_verifypeer = 0L))
}

f_adjust_types <- function(z)
{
  names(z) <- c("Date", paste0("mo", c(1, 2, 3, 6)), paste0("yr0", c(1, 2, 3, 5, 7)), 
              paste0("yr", c(10, 20, 30)))
  z$Date <- as.Date(z$Date, format = "%m/%d/%y")
  suppressWarnings(z$mo1 <- as.numeric(z$mo1))
  suppressWarnings(z$mo2 <- as.numeric(z$mo2))
  suppressWarnings(z$mo3 <- as.numeric(z$mo3))
  suppressWarnings(z$mo6 <- as.numeric(z$mo6))
  suppressWarnings(z$yr01 <- as.numeric(z$yr01))
  suppressWarnings(z$yr02 <- as.numeric(z$yr02))
  suppressWarnings(z$yr03 <- as.numeric(z$yr03))
  suppressWarnings(z$yr05 <- as.numeric(z$yr05))
  suppressWarnings(z$yr07 <- as.numeric(z$yr07))
  suppressWarnings(z$yr10 <- as.numeric(z$yr10))
  suppressWarnings(z$yr20 <- as.numeric(z$yr20))
  suppressWarnings(z$yr30 <- as.numeric(z$yr30))
  return(z)
}

file_name <- "Fed_data.Rdata"
if (file.exists(file_name))
{
  load(file = file_name)
} else
{
  my_url <- "https://www.treasury.gov/resource-center/data-chart-center/interest-rates/Pages/TextView.aspx?data=yieldYear&year=2018"
  X2018 <- read_html(httr::GET(my_url))
  Y2018 <- X2018 %>% rvest::html_node("table.t-chart") %>% rvest::html_table()
  Y2018 <- f_adjust_types(Y2018)
  
  my_url <- "https://www.treasury.gov/resource-center/data-chart-center/interest-rates/Pages/TextView.aspx?data=yieldYear&year=2009"
  X2009 <- read_html(httr::GET(my_url))
  Y2009 <- X2009 %>% rvest::html_node("table.t-chart") %>% rvest::html_table()
  Y2009 <- f_adjust_types(Y2009)
  
  my_url <- "https://www.treasury.gov/resource-center/data-chart-center/interest-rates/Pages/TextView.aspx?data=yieldYear&year=2006"
  X2006 <- read_html(httr::GET(my_url))
  Y2006 <- X2006 %>% rvest::html_node("table.t-chart") %>% rvest::html_table()
  Y2006 <- f_adjust_types(Y2006)
  
  my_url <- "https://www.treasury.gov/resource-center/data-chart-center/interest-rates/Pages/TextView.aspx?data=yieldAll"
  X <- read_html(httr::GET(my_url))
  Y <- X %>% rvest::html_node("table.t-chart") %>% rvest::html_table()
  Y <- f_adjust_types(Y)
  
  save(Y, Y2006, Y2009, Y2018, file = file_name)
}

```

## Risk Free Yield

The risk-free rate of return is the theoretical rate of return of an investment with zero risk.  The risk free yield for a particular duration is represented by the treasury 
yield curve.  In reality, there is some
risk inherent in U.S. Government securities, but it is accepted as the risk-free
alternative to other investments.

The Federal Open Market committee and the Federal Reserve Board of Governors, or the 
"Fed" sets short term interest rates.  The market sets the yield for the longer term
securities according to supply, demand, and projections about longer term interest
rates.

In theory, the risk-free rate is the minimum return an investor expects for any 
investment because any investment with greater risk should yield a higher rate to compensate for it. [1](https://www.investopedia.com/terms/r/risk-freerate.asp#ixzz5S2zxvxXx )

Treasury maturities:

* Treasury Bills have maturity <= 1 yr.  They are sold at a discount to face
value.  The face value is returned at maturity.
* Treasury Notes have maturity 2 - 10 yrs.  Yield a fixed
interest rate with payments every 6 months.
* Treasury Bonds, 20 - 30 yrs.  Yield a fixed
interest rate with payments every 6 months.  

#### Market expectations Theory

Market expectations theory postulates that the yield curve shape depends on 
market participant's expectations of future rates.  Under this theory,
a series of short term investments should have a return close to the long term
return because there is no differential risk between the two.  When this does
not hold, it indicates a short term opportunity which will be corrected by the
market.

#### Liquidity premium Theory

The liquidity premium theory also believes that there is a liquidity premium
inherent in holding long-term bonds.  There is risk that the interest rate
expetations in the long term are wrong and there is an opporutnity cost in
investing capital over a long term.  

#### Preferred Maturity Theory or Preferred Habitat Theory

This theory holds that investors have a preferred time horizon (short or long)
and that investing outside of that time horizon deserves a premium.  If short
term investments are preferred on average, then longer term investments should
yield higher rates.  

## Yield curve types

The yield curve generally takes three shapes:
* Normal, rising rates with longer maturites
* Flat
* Inverted, falling rates with longer maturities.  An inverted yield curve is
often a signal of an impending recession.

```{r TreasuryPlot, echo=FALSE}
x <- c(1/12, 2/12, 3/12, 6/12, c(1,2,3,5,7,10,20,30))
x_labels <- c("1mo", "2mo", "3mo", "6mo", 1, 2, 3, 5, 7, 10, 20, 30)

Y1 <- rbind(subset(Y2018, Date == as.Date("2018-01-02")),
            subset(Y2009, Date == as.Date("2009-11-27")),
            subset(Y2006, Date == as.Date("2006-11-15")))
df1 <- data.frame(x = rep(x, each = nrow(Y1)),
                 y = unlist(Y1[,-1], use.names = FALSE),
                 id = rep(c("Flat 1/2/2018", "Normal 11/27/2009", "Inverted 11/15/2006"), times = length(x)))
g1 <- ggplot(df1, aes(x = x, y = y, group = id, col = id)) + 
  geom_line() + geom_point() +
  ylim(0, 6) + ylab("Percent") +
  scale_x_log10(limits = c(0.08, 31), breaks = x, labels = x_labels, name = "Years") +
  theme_bw() + theme(legend.title = element_blank()) +
  ggtitle("Example Yield Curves (Note the logaritmic scale)")
plot(g1)

```

## Yield Curve Changes Throughout the Year and Over Time

```{r TreasuryPlot2018, echo=FALSE, warning=FALSE}
Y1 <- subset(Y2018, Date >= as.Date("2018-01-01"))
df1 <- data.frame(x = rep(x, each = nrow(Y1)),
                 y = unlist(Y1[,-1], use.names = FALSE),
                 date = rep(factor(as.character(Y1[,1])), times = length(x)))
df2 <- data.frame(x = x,
                  y = unlist(Y1[1, -1]),
                  date = Y1$Date[1])
g1 <- ggplot(df1, aes(x = x, y = y, group = date)) + 
  geom_line(col = "grey") + 
  geom_line(aes(x = x, y = y, group = date), data = df2, col = "green") +
  ylim(0, 4) + ylab("Percent") +
  scale_x_log10(limits = c(0.08, 31), breaks = x, labels = x_labels, name = "Years") +
  ggtitle("Yield Curve Changes in 2018") + theme_bw()
plot(g1)

Y1 <- subset(Y, day(Date) == 1) # get the first of each month not a weekend
df1 <- data.frame(x = rep(x, each = nrow(Y1)),
                 y = unlist(Y1[,-1], use.names = FALSE),
                 date = rep(factor(as.character(Y1[,1])), times = length(x)),
                 ids = factor(rep(x, each = nrow(Y1))))
g1 <- ggplot(df1, aes(x = x, y = y, group = date)) + 
  geom_line(aes(frame = date, ids = ids), col = "blue") + 
  geom_point(aes(frame = date, ids = ids), col = "blue", size = 1.5) +
  ylim(0, 9) + ylab("Percent") +
  scale_x_log10(limits = c(0.08, 30), breaks = x, 
                labels = x_labels, name = "Years") +
  theme_bw()
ggplotly(g1)

df1 <- reshape::melt(Y, id.vars = "Date")
names(df1) <- c("Date", "Duration", "yield")
g1 <- ggplot(data = df1) + 
  geom_rect(aes(xmin = as.Date("2007-12-07"), 
                xmax = as.Date("2009-06-02"), 
                ymin = 0, ymax = Inf), fill = "lightgrey") +
  geom_rect(aes(xmin = as.Date("1990-07-01"), 
                xmax = as.Date("1991-03-31"), 
                ymin = 0, ymax = Inf), fill = "lightgrey") +
  geom_rect(aes(xmin = as.Date("2001-03-01"), 
                xmax = as.Date("2001-11-30"), 
                ymin = 0, ymax = Inf), fill = "lightgrey") +
  geom_line(aes(x = Date, y = yield, group = Duration, col = Duration)) +
  theme_bw() +
  ylim(0, 9) + ylab("Percent") +
  ggtitle("Yields on Each Treasury Duration Over Time")
plot(g1)

```

Note that the yield curve inverts (the 10 yr treasury is lower yield than
the 2 year treasury) just before a recession (shaded area).

```{r echo=FALSE, warning=FALSE}

df1 <- data.frame(Date = Y$Date,
                  yieldSpread = Y$yr10 - Y$yr02)
g1 <- ggplot(df1) + 
  geom_rect(aes(xmin = as.Date("2007-12-07"), 
                xmax = as.Date("2009-06-02"), 
                ymin = 0, ymax = Inf), fill = "lightgrey") +
  geom_rect(aes(xmin = as.Date("1990-07-01"), 
                xmax = as.Date("1991-03-31"), 
                ymin = 0, ymax = Inf), fill = "lightgrey") +
  geom_rect(aes(xmin = as.Date("2001-03-01"), 
                xmax = as.Date("2001-11-30"), 
                ymin = 0, ymax = Inf), fill = "lightgrey") +
  theme_bw() + ylab("Difference in Rate Between 10 and 2 yr Treasuries") +
  geom_line(aes(x = Date, y = yieldSpread)) +
  geom_hline(aes(yintercept = 0), col = "red") +
  ggtitle("Inverted Yield Curves Generally Preceed Recession")
plot(g1)

```


## Starting a Bank

### Example Yield Curve

* All rates in this section are annualized.
* All loans and deposit products are paid or charged interest at the end of each 
year.  The entire principle and interest are paid back at the end of the term.

```{r echo=FALSE}
df1 <- data.frame(x = x,
                  y = c(1.5, 1.5, 1.6, 1.7, 1.85, 2.0, 2.2, 2.5, 3.0, 3.5, 4.0, 4.5))

g1 <- ggplot(df1, aes(x = x, y = y)) + 
  geom_line() + geom_point() +
  ylim(0, 5) + ylab("Percent") +
  scale_x_log10(limits = c(0.08, 31), breaks = x, labels = x_labels, name = "Years") +
  theme_bw()
plot(g1)

```

### One CD, one secured loan, matched term and some equity

```{r echo=FALSE}
cd_rate <- 0.0050
cd_value <- 100000
loan_rate <- 0.03
loan_value <- 200000
```

* Accept a one year CD at 0.50% for $100,000
* Take $100,000 of shareholder investment
* Loan a one year secured loan at 3.0% for $200,000

* Interest Income = `r scales::dollar(loan_rate*loan_value)`
* Interest Expense = `r scales::dollar(cd_rate*cd_value)`
* Net Interest Income = Spread Income = `r scales::dollar(loan_rate*loan_value-cd_rate*cd_value)`

```{r echo=FALSE}
g1 <- ggplot(df1, aes(x = x, y = y)) + 
  geom_line() + geom_point() +
  ylim(0, 5) + ylab("Percent") +
  scale_x_log10(limits = c(0.08, 31), breaks = x, labels = x_labels, name = "Years") +
  annotate("point", x = 1, y = 0.5, col = "blue") +
  annotate("point", x = 1, y = 3, col = "red") +
  annotate("segment", x = 1, xend = 1, y = 0.5, yend = 3, col = "green") +
  theme_bw()
plot(g1)
```


#### Risks

* Can I do this again at the end of the term?
* If the loan defaults, then equity may be lost to repay the depositors.

### One Loan and a shorter term CD

```{r echo=FALSE}
cd_rate <- 0.0030
cd_value <- 100000
loan_rate <- 0.0315
loan_value <- 200000
```

In order to make more spread income, we can shorten the maturity on deposits and increase
the maturity of the loans.

* Accept a six month CD at 0.35% annual for $100,000 every 6 months
* Take $100,000 of shareholder investment
* Loan a two year secured loan at 3.15% annual for $200,000

Each year,

* Interest Income = `r scales::dollar(loan_rate*loan_value)`
* Interest Expense = `r scales::dollar(cd_rate*cd_value)`
* Net Interest Income = Spread Income = `r scales::dollar(loan_rate*loan_value-cd_rate*cd_value)`

```{r echo=FALSE}
g1 <- ggplot(df1, aes(x = x, y = y)) + 
  geom_line() + geom_point() +
  ylim(0, 5) + ylab("Percent") +
  scale_x_log10(limits = c(0.08, 31), breaks = x, labels = x_labels, name = "Years") +
  annotate("point", x = 0.5, y = 0.35, col = "blue") +
  annotate("point", x = 2, y = 3.15, col = "red") +
  annotate("segment", x = 0.5, xend = 0.5, y = 0.35, yend = 1.7, col = "green") +
  annotate("segment", x = 2, xend = 2, y = 2, yend = 3.15, col = "green") +
  theme_bw()
plot(g1)
```

#### Risks

* interest rate risk that rates will rise before I need to issue new CDs
which will compress the spread

### Duration

Duration represents the sensitivity of a portfolio to future interest rate increases.  One
formulation is caluclated as the average maturity weighted by the present value
of each payment.

$$\textit{Macaulay Duration} = \frac{\sum\limits_{j=1}^n t_j PV_j}{\sum\limits_{j=1}^n PV_j}$$

where:

* $t_i$ is the time of the i^{th} cash flow
* $PV_i$ is the present value of the i^{th} cash flow

#### Duration Gap

The duration gap is the difference between the assest and liability gap and gives
a measure for the change in portfolio value or Net Worth (NW) given a change in interest rates.

$$D_{gap} = D_a - \frac{\sum a_j}{\sum l_j} D_l$$

$$\Delta NW = - D_{gap} * \frac{\Delta i}{1 + i}$$

```{r echo=FALSE, results=FALSE}
macaulay_duration <- function(times, cash_flows, discount_rate_per_period)
{
  assertthat::assert_that(length(times) == length(cash_flows))
  discount_factor <- (1 + discount_rate_per_period)^times
  V <- sum(cash_flows / discount_factor)
  return(sum(times * cash_flows / discount_factor) / V)
}
assertthat::assert_that(all.equal(
  macaulay_duration(1:6, c(rep(30, 5), 1030), 0.03), 5.58,
  tolerance = 0.001))

yield_to_maturity <- function(periods_remaining, coupon_payment, 
                              bond_price, maturity_value)
{
  f <- function(i, n, bp, cf, mv)
  {
    (cf*(1 - (1/(1 + i)^n))/i + mv / (1 + i)^n - bp)^2
  }
  o1 <- optimize(f, interval = c(0, 1000), n = periods_remaining, bp = bond_price,
              cf = coupon_payment, mv = maturity_value)
  return(o1$minimum)
}
assertthat::assert_that(all.equal(yield_to_maturity(5, 2.5, 95.92, 100), 0.034, 
                                  tolerance = 0.001))
```

#### Duration of the Portfolio

```{r echo=FALSE}
duration_l <- macaulay_duration(1, 100000*(1 + 0.0035/2), 0.0035/2) * 0.5 # 1/2 to change from 6 month periods to 1 year periods
duration_a <- macaulay_duration(1:2, c(0.0315*200000, 200000*(1 + 0.0315)), 0.0315)
duration_gap <- duration_a - cd_value / loan_value * duration_l
change_worth <- -1 * duration_gap * 0.01 / (1 + 0.0175) # 1.75% is an average interest rate
```

* Duration of the liabilities = `r signif(duration_l, 3)` years
* Duration of the assets = `r signif(duration_a, 3)` years
* Duration gap = `r signif(duration_gap, 3)` years

If rates rise from the current environment of 1.75% to 2.75% then the value of the
portfolio decreases by `r scales::percent(change_worth)`.

## Balance Sheet and Income Statement Concepts

### Balance Sheet

$$a = l + q$$
$$a = \sum a_j,\ \ \ l = \sum l_j,\ \ \ q = \sum q_j$$

* $a$ = Total Assets
* $l$ = Total Liabilities
* $q$ = Total Equity
* $j$ = individual asset, liability,or equity

$$\langle a \rangle = \frac{1}{t_2 - t_1}\int_{t_1}^{t_2}a(t)dt$$

* $\langle a \rangle$ = Average Assets or Time-Averaged Assets
* similaryly, $\langle l \rangle$ and $\langle q \rangle$

### Income Statement

$$i_{\textit{PTPP}} = i_{nI} + i_{I} - e_{I} - e_{nI}$$
$$i_{NI} = i_{I} - e_{I}$$
$$\textit{Total Revenue} = i_{I} + i_{nI}$$

* $i$ = Income
* $e$ = Expense
* $PTPP$ = Pre-Tax Pre-Provision
* $nI$ = Non-Interest
* $I$ = Interest
* $NI$ = Net Interest

$$i_{\textit{NIBT}} = i_{\textit{PTPP}} - e_{\textit{PLL}}$$

* $NIBT$ = Net Income Before Taxes.
* $PLL$ = Provision for Loan Losses

$$i_{N} = i_{\textit{NIBT}} - e_{\textit{Tax}}$$
$$i_{\textit{NIATC}} = i_{N} - e_{\textit{Pref Div}}$$

* $N$ = Net
* $NIATC$ = Net Income Available to Common or available to common shareholders
* $Pref\ Div$ = Dividends for Preferred shared

```{r waterfalls}
g <- waterfall(values = c(10, -2, 8, -4, -1, -0.4, -0.2),
          labels = c("Interest\nIncome", "Interest\nExpense", "Non-Interest\nIncome",
                     "Non-Interest\nExpense", "Provision for\nLoan Losses",
                     "Tax", "Preferred\nDividends"),
          calc_total = TRUE,
          rect_width = 0.5,
          print_plot = FALSE,
          rect_text_labels = character(7),
          total_rect_text = "") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
        axis.ticks.x = element_blank())

g + annotate("text", x = 2.5, y = 8.2, label = "Net Income", angle = 90, hjust = 0) +
  annotate("text", x = 4.5, y = 12.2, label = "PTPP", angle = 90, hjust = 0) +
  annotate("text", x = 5.5, y = 11.2, label = "NIBT", angle = 90, hjust = 0) +
  annotate("text", x = 6.5, y = 10.8, label = "NI", angle = 90, hjust = 0) +
  annotate("text", x = 7.5, y = 10.6, label = "NIATC", angle = 90, hjust = 0)
```

### Performance Measures

```{r echo=FALSE}
make_performance_graph <- function(key, xlabel, show_zero = TRUE)
{
  URL <- "https://fred.stlouisfed.org/graph/fredgraph.csv?drp=0&mode=fred&id=USROE&cosd=1984-01-01&coed=2018-04-01&fq=Quarterly%2C%20End%20of%20Period&fam=avg&vintage_date=2018-10-14&revision_date=2018-10-14&nd=1984-01-01"
  URL_parsed <- httr::parse_url(URL)
  URL_parsed$query$id <- key
  URL <- httr::build_url(URL_parsed)
  
  data_page <- httr::GET(URL)
  suppressMessages(csv_data <- httr::content(data_page, as = "parsed", type = "text/csv", 
                            encoding = "UTF-8"))
  
  g1 <- ggplot(csv_data, aes_string(x = "DATE", y = key)) + 
      xlab("") + ylab(xlabel) + theme_bw() +
      geom_rect(aes(xmin = as.Date("2007-12-07"), 
                    xmax = as.Date("2009-06-02"), 
                    ymin = -Inf, ymax = Inf), fill = "lightgrey") +
      geom_rect(aes(xmin = as.Date("1990-07-01"), 
                    xmax = as.Date("1991-03-31"), 
                    ymin = -Inf, ymax = Inf), fill = "lightgrey") +
      geom_rect(aes(xmin = as.Date("2001-03-01"), 
                    xmax = as.Date("2001-11-30"), 
                    ymin = -Inf, ymax = Inf), fill = "lightgrey") +
      geom_line()
  if (show_zero)
    g1 <- g1 + geom_hline(yintercept = 0, col = "red")

  plot(g1)
}
```

$$\eta = \frac{i_{nI} + i_{I} - e_{I} - e_{nI}}{i_{nI} + i_{I} - e_{I}}$$
$$\textit{efficiency ratio} = (1-\eta) = \frac{e_{nI}}{i_{nI} + i_{I} - e_{I}}$$

```{r echo=FALSE}
make_performance_graph("DDEI07USA156NWDB", "US Average Efficiency Ratio", 
                       show_zero = FALSE)
```


$$\textit{ROE} = \frac{i_{\textit{NIATC}}}{\langle e \rangle}$$

```{r echo=FALSE}
make_performance_graph("USROE", "US Averge Return on Equity")
```

$$\textit{ROA} = \frac{i_{\textit{NIATC}}}{\langle a\rangle}$$

```{r echo=FALSE}
make_performance_graph("USROA", "US Averge Return on Average Assets")
```


$$\textit{ROE} = (\textit{Leverage})(\textit{ROA})$$

$$\textit{ROE} =  (\textit{Asset Yield})(\textit{Profit Margin})(\textit{Leverage})$$
$$\textit{ROE} = \frac{\textit{Total Revenue}}{\textit{Avg Total Assets}}\frac{\textit{Net Income}}{\textit{Total Revenue}}\frac{\textit{Avg Total Assets}}{\textit{Avg Common Equity}}$$
$$\textit{ROE} = \frac{i_{nI}+i_{I}}{\langle a \rangle}\frac{i_{\textit{NIATC}}}{i_{nI}+i_{I}}\frac{\langle a \rangle}{\langle e \rangle}$$
$$\textit{NIM} = \frac{i_I - e_I}{\langle a_{\textit{earning}} \rangle}$$

* $NIM$ = Net Interest Margin
* $\langle a_{\textit{earning}} \rangle$ = Average Earning Assets

```{r echo=FALSE}
make_performance_graph("USNIM", "US Average Net Interest Margin", show_zero = FALSE)
```

## Dictionary

* Yield - The yield is the income return on an investment, such as the interest or dividends received from holding a particular security. The yield is usually expressed as an annual percentage rate based on the investment's cost, current market value or face value. Yields may be considered known or anticipated depending on the security in question as certain securities may experience fluctuations in value. {https://www.investopedia.com/terms/y/yield.asp}
* APY - The annual percentage yield (APY) is the effective annual rate of return taking into account the effect of compounding interest. APY is calculated by $(1 + periodic rate)^{Periods} - 1$  The resultant percentage assumes that the funds will remain in the investment vehicle for a full 365 days. {https://www.investopedia.com/terms/a/apy.asp}
* APR - An annual percentage rate (APR) is the annual rate charged for borrowing or earned through an investment, and is expressed as a percentage that represents the actual yearly cost of funds over the term of a loan. This includes any fees or additional costs associated with the transaction but does not take compounding into account. As loans or credit agreements can vary in terms of interest-rate structure, transaction fees, late penalties and other factors, a standardized computation such as the APR provides borrowers with a bottom-line number they can easily compare to rates charged by other lenders. {https://www.investopedia.com/terms/a/apr.asp}

#### Bond terminology

* Coupon rate - The yield paid by a fixed income security.  If a bond is issued with a \$1,000 face value
and a \$25 coupon every six months, then the annual interest rate is $5\% = \frac{2*25}{1000}$
* Market rate - The yield paid by an equivalent maturity in the market
* Yield to Maturity - This is the yield paid by the bond using the market value
of the bond as the denominator.  For example, a \$100 face value or par value bond has
a \$5 coupon payment twice a year or a 10\% yield.  The bond trades for \$90 so the yield
to maturity on the remaining payments is $\frac{10}{90} = 11.1\%$ 
* Zero Coupon Bond - a bond that pays no periodic interest and instead pays the 
principal and interest at bond maturity.
